The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-02-13 Manuscript/manuscript.tex
Update manuscript.tex

There are a few examples of natural experiments in basketball. \citet{Harville} studied the
effect of home-court advantage using the 1991-1992 college basketball season.
Unlike the NBA, it is not uncommon to have a few games played at neutral sites
during the college basketball season. This allowed them to construct two samples,
one of home teams and one of neutral teams. They formulated their study in a
regression predicting the expected difference in score for home teams.
They set up their study to find if the home teams won games by more points when
they had home-court advantage vs.~when playing at neutral court. This study
concluded with evidence supporting home-court advantage. Also, \cite{Boudreaux} is 
able to construct a natural experiment using the Los Angeles Lakers and Los Angeles 
Clippers. Since these two teams share a home stadium, many factors like travel and 
familiarity are nullified. However, the designated home team has larger crowd support
due to attendance from their season ticket holders. When they single out the effect 
of having a sympathetic crowd, \cite{Boudreaux} estimate crowd effects
increase chance of winning 21--22.8 percentage pointts.

>>>>

There are a few examples of natural experiments in basketball. \citet{Harville} studied the
effect of home-court advantage using the 1991-1992 college basketball season.
Unlike the NBA, it is not uncommon to have a few games played at neutral sites
during the college basketball season. This allowed them to construct two samples,
one of home teams and one of neutral teams. They formulated their study in a
regression predicting the expected difference in score for home teams.
They set up their study to find if the home teams won games by more points when
they had home-court advantage vs.~when playing on a neutral court. This study
concluded with evidence supporting home-court advantage. Also, \cite{Boudreaux}
is able to construct a natural experiment using the Los Angeles Lakers and Los
Angeles Clippers. Since these two teams share a home stadium, many factors like 
travel and familiarity are nullified. However, the designated home team has larger
crowd support due to attendance from their season ticket holders. When they
single out the effect of having a sympathetic crowd, \cite{Boudreaux} estimate crowd 
effects increase the chance of winning 21--22.8 percentage points.
